\documentclass[main.tex]{subfiles}

\begin{document}

\subproblem{}\label{2a}
\[A \subset B \land A \subset C \iff A \subset (B \cup C)\]
\begin{thm}[Double implication fails in~\ref{2a}]
	\(A \subset B \land A \subset C \centernot\iff A \subset (B \cup C)\)
\end{thm}
\begin{proof}
	For double implication to hold, each predicate must imply the other. We
	will explore whether
	\(A \subset (B \cup C) \implies A \subset B \land A \subset C\).

	Consider \(A \subset (B \cup C)\). Choose
	\(A = \{m | m = 3k, k \in \mathbb{Z}\}\),
	\(B = \{e | e = 2k, k \in \mathbb{Z}\}\),
	and \(C = \{o | o = 2k + 1, k \in \mathbb{Z}\}\) (i.e., \(A\) is the set
	of multiples of	3, \(B\) is the set of all evens, and \(C\) is the set
	of all odds). Since all integers are even or odd, we can say that it is
	indeed the case that \(A \subset (B \cup C)\) holds for our choices of
	\(A\), \(B\), and \(C\). Suppose
	\(A \subset (B \cup C) \implies A \subset B \land A \subset C\). Since
	we have already shown that the antecedent holds for our choices of
	\(A\), \(B\), and \(C\), this would require the consequent to be true as
	well. So both \(A \subset B\) and \(A \subset C\). Considerring just
	\(A \subset B\), this would mean that the set of multiples of 3 is a
	subset of the evens. This would imply that \(\forall x \in A, x \in B\).
	Now note that \(3 = x \in A\) because 3 is a multiple of 3. However,
	\(3 = x \notin B\) as 3 is not even. This contradicts our requirement
	that for any \(x \in A\), it is also the case that \(x \in B\). So our
	supposition is false, and
	\(A \subset (B \cup C) \centernot\implies A \subset B \land A \subset C\).

	Since we have demonstrated that one of the predicates does not imply the
	other predicate, we have therefore established that the double
	implication fails as well.
\end{proof}

\begin{thm}[LHS implies RHS in~\ref{2a}]
	\(A \subset B \land A \subset C \implies A \subset (B \cup C)\)
\end{thm}
\begin{proof}
	It is given that \(A \subset B\) and \(A \subset C\). Considerring just
	\(A \subset B\), it is either the case that \(A = \emptyset\) or
	\(\exists x \in A \implies x \in B\). In the trivial case that
	\(A = \emptyset\), \(A \subset (B \cup C)\) since the empty set is a
	subset of all sets. In the case that \(A\) is not empty, then we can say
	that \(\exists x \in A \implies (x \in B \lor x \in C)\) by disjunctive
	inclusion. By the definition of set union, we have that
	\(x \in (B \cup C)\). So
	\(A \neq \emptyset \implies A \subset (B \cup C)\). Since
	\(A \subset (B \cup C)\) in all cases derived from our assumptions, we
	have therefore demonstrated that
	\(A \subset B \land A \subset C \implies A \subset (B \cup C)\).
\end{proof}

\end{document}
