\documentclass[main.tex]{subfiles}

\begin{document}

\subproblem{}\label{s2p2f}

Show that functions preserve unions. Symbolically, that is:
\[f(A_0 \union A_1) = f(A_0) \union f(A_1)\]

\begin{thm}
	Set union distributes through the image of a function. Symbolically,
	given \(\mapping{f}{A}{B}\) and \(A_0 \subset A\) and \(A_1 \subset A\),
	that is:
	\[f(A_0 \union A_1) = f(A_0) \union f(A_1)\]
\end{thm}
\begin{proof}
	Let \(A\) and \(B\) be sets, let \(f\) be a mapping from \(A\) to \(B\),
	and let \(A_0\) and \(A_1\) be a subsets of \(A\).

	First, assume \(y\) is in \(f(A_0 \union A_1)\). By the definition of
	image, we know that there exists some \(x\) in \(A_0 \union A_1\) such
	that \(y = f(x)\). We know that this \(x\) is in \(A_0\) or in \(A_1\)
	(or both) by the definition of set union. Recalling that \(y = f(x)\),
	we see that \(y\) is in \(f(A_0)\) or in \(f(A_1)\) (or both) by the
	definition of image. Taking the set union, we have that \(y\) is in
	\(f(A_0) \union f(A_1)\). Thus \(f(A_0 \union A_1)\) is a subset of
	\(f(A_0) \union f(A_1)\).

	Next, assume \(y\) is in \(f(A_0) \union f(A_1)\). By the definition of
	set union, we have that \(y\) is in \(f(A_0)\) or in \(f(A_1)\) (or
	both). Given the definition of image, we know that there exists either
	some \(x\) in \(A_0\) such that \(y = f(x)\), or there exists some
	\(x'\) in \(A_1\) such that \(y = f(x')\) (or both). Should both exist,
	we would not know whether \(x\) and \(x'\) have the same value as we
	do not know if \(f\) is injective, but in any case we know that applying
	\(f\) to whichever value exists yields \(y\). Now we know that either
	\(x\) or \(x'\) (or both) are in \(A_0 \union A_1\) by the definition of
	set intersection. Recalling that both \(y = f(x)\) and \(y = f(x')\), we
	see that \(y\) is in \(f(A_0 \union A_1)\) by the definition of image.
	Thus \(f(A_0) \union f(A_1)\) is a subset of \(f(A_0 \union A_1)\).

	As we have shown that \(f(A_0 \union A_1)\) and \(f(A_0) \union f(A_1)\)
	are subsets of each other, we have demonstrated set equality.
\end{proof}

\end{document}
