\documentclass[main.tex]{subfiles}

\begin{document}

\subproblem{}\label{s2p2c}

Show that function inversion preserves intersection. Symbolically, that is:
\[\inverse{f}(B_0 \intersect B_1) = \inverse{f}(B_0) \intersect \inverse{f}(B_1)\]

\begin{thm}
	Set intersection distributes through the preimage of a function.
	Symbolically, given \(\mapping{f}{A}{B}\) and \(B_0 \subset B\) and
	\(B_1 \subset B\), that is:
	\[\inverse{f}(B_0 \intersect B_1) = \inverse{f}(B_0) \intersect \inverse{f}(B_1)\]
\end{thm}
\begin{proof}
	Let \(A\) and \(B\) be sets, let \(f\) be a mapping from \(A\) to \(B\),
	and let \(B_0\) and \(B_1\) be a subsets of \(B\).

	First, assume \(x\) is in \(\inverse{f}(B_0 \intersect B_1)\). By the
	definition of preimage, we know that there is some \(y = f(x)\) in
	\(B_0 \intersect B_1\). Also, we know that both \(y\) is in \(B_0\) and
	\(y\) is in \(B_1\) given the definition of set intersection. Recalling
	that \(y = f(x)\), the definition of preimage gives us both \(x\) in
	\(\inverse{f}(B_0)\) and \(x\) in \(\inverse{f}(B_1)\). So \(x\) is in
	\(\inverse{f}(B_0) \intersect \inverse{f}(B_1)\) by the definition of
	set intersection. Thus \(\inverse{f}(B_0 \intersect B_1)\) is a subset
	of \(\inverse{f}(B_0) \intersect \inverse{f}(B_1)\).

	Next, assume \(x\) is in
	\(\inverse{f}(B_0) \intersect \inverse{f}(B_1)\). By the definition of
	set intersection, we have that both \(x\) is in \(\inverse{f}(B_0)\) and
	\(x\) is in \(\inverse{f}(B_1)\). By the definition of preimage, we know
	that there is some \(y = f(x)\) in \(B_0\) and some \(y' = f(x)\) in
	\(B_1\). Fortunately, we know that it is indeed the case that
	\(y = f(x) = y'\) due to the rule of assignment. Since \(y\) is in both
	\(B_0\) and \(B_1\), we can see that \(y\) is in \(B_0 \intersect B_1\)
	by definition. Recalling that \(y = f(x)\), we have that \(x\) is in
	\(\inverse{f}(B_0 \intersect B_1)\) by the definition of preimage. So
	\(\inverse{f}(B_0) \intersect \inverse{f}(B_1)\) is a subset of
	\(\inverse{f}(B_0 \intersect B_1)\).

	As we have shown that \(\inverse{f}(B_0 \intersect B_1)\) and
	\(\inverse{f}(B_0) \intersect \inverse{f}(B_1)\) are subsets of each
	other, we have also demonstrated set equality.
\end{proof}

\end{document}
